Scalar on Function Regression \\ with Applications to Near-Infrared Spectroscopy

### 2022-01-16 Presentation/slides.tex
push presentation changes

		\begin{itemize}
    		\item Four combinations with different number of cubic bspline basis-function $n_{basis} \in \{4,5, \dots ,25\}$ and fourier functions $\{1,3, \dots, 25\}$ to perform regression using basis expansion and the FPCR approach.
			\item Compare results via criteria (CV, Mallows CP, ...)

@@

	\begin{frame}{Simulation - Interpretation of Results}\label{Results}
		\textbf{Basis Expansion Regression}
		\begin{itemize}
    			\item Smooth true coefficient functions requires smaller number of $n_{basis}$ and vice versa
    			\item Setup with higher noise requires smoother function.
    			\item  Bspline setup performs overall a bit better.
		\end{itemize}

		\textbf{FPCR}
    	\begin{itemize}
    		\item Two PC enough to explain variation.
    		\item Results quite similar, but bspline setup better for smooth function with noisy response.
    	\end{itemize}

    	Overall, fourier setup has lower complexity.

@@

	\begin{frame}{Application Setup}
		\begin{itemize}
			\item Use insights from the simulation study to uncover dependence.
			\item Similar setup, but using only bspline basis expansion and initial 60 spectral curves.
			\item Validation set approach:	Scores of test data needs to be estimated by the training data. 
			\item Report results by MSE scaled by variance.
		\end{itemize}
	\end{frame}

@@

	\begin{frame}{Simulation Results - bspline basis expansion}\label{Simulation}
		\begin{table}
			\centering
			\resizebox*{\columnwidth}{!}{%
				\begin{tabular}{lllllll}
					\cline{2-6}
					& \textbf{f1\_e1\_spline}                 & \textbf{f1\_e2\_spline}                 & \textbf{f2\_e1\_spline}                   & \textbf{f2\_e2\_spline}                 & \textbf{n\_basis} &  \\ \cline{2-6}
					& 2.1318                        & {\color[HTML]{FE0000} 71.71} & 0.6082                        & 1.5345                        & 4                &  \\
					& 2.0076                        & 71.9395                      & 0.3427                        & 1.2906                        & 5                &  \\
					& {\color[HTML]{FE0000} 1.9937} & 72.2563                      & 0.2456                        & 1.2014                        & 6                &  \\
					& 2.0365                        & 73.7857                      & 0.2797                        & 1.2495                        & 7                &  \\
					& 2.1861                        & 79.0485                      & 0.1044                        & 1.1458                        & 8                &  \\
					& 2.0511                        & 74.1784                      & 0.0356                        & {\color[HTML]{FE0000} 1.0217} & 9                &  \\
					& 2.1052                        & 76.1884                      & 0.0297                        & 1.0393                        & 10               &  \\
					& 2.1012                        & 76.4031                      & {\color[HTML]{FE0000} 0.0296} & 1.0425                        & 11               &  \\
					& 2.3815                        & 86.1707                      & 0.037                         & 1.1819                        & 12               &  \\
					& 2.2114                        & 80.6208                      & 0.0363                        & 1.1024                        & 13               &  \\
					& 2.4495                        & 87.6977                      & 0.038                         & 1.2126                        & 14               &  \\
					& 2.2887                        & 83.4755                      & 0.0315                        & 1.1363                        & 15               &  \\
					& 2.5491                        & 93.593                       & 0.0352                        & 1.2652                        & 16               
				\end{tabular}%
			}
		\end{table}
		\hyperlink{Results}{\beamergotobutton{Results}}
	\end{frame}

	\begin{frame}{Simulation Results - fourier basis expansion}
		\begin{table}
			\centering
			\resizebox*{\columnwidth}{!}{%
				\begin{tabular}{lllllll}
					\cline{2-6}
					& \textbf{f1\_e1\_spline}                 & \textbf{f1\_e2\_spline}                 & \textbf{f2\_e1\_spline}                   & \textbf{f2\_e2\_spline}                 & \textbf{n\_basis} &  \\ \cline{2-6}
					& 0                            & 0                              & 0                            & 0                             & 1                &  \\
					& 2.0292                       & {\color[HTML]{FE0000} 72.0085} & 0.512                        & 1.4747                        & 3                &  \\
					& {\color[HTML]{FE0000} 2.022} & 72.6017                        & 0.1616                       & 1.1375                        & 5                &  \\
					& 2.0355                       & 73.1836                        & 0.0293                       & {\color[HTML]{FE0000} 0.9907} & 7                &  \\
					& 2.062                        & 73.9631                        & {\color[HTML]{FE0000} 0.029} & 0.9994                        & 9                &  \\
					& 2.0881                       & 75.0921                        & 0.0291                       & 1.0139                        & 11               &  \\
					& 2.0997                       & 75.9422                        & 0.0294                       & 1.0291                        & 13               &  \\
					& 2.1087                       & 76.7123                        & 0.0298                       & 1.0371                        & 15               &  \\
					& 2.1301                       & 77.4908                        & 0.03                         & 1.0398                        & 17               &  \\
					& 2.1535                       & 78.3943                        & 0.0303                       & 1.0509                        & 19               &  \\
					& 2.1775                       & 79.2058                        & 0.0307                       & 1.0617                        & 21               &  \\
					& 2.2058                       & 80.3801                        & 0.031                        & 1.077                         & 23               &  \\
					& 2.2372                       & 81.509                         & 0.0315                       & 1.0905                        & 25               & 
				\end{tabular}%
			}
		\end{table}
		\hyperlink{Results}{\beamergotobutton{Results}}
	\end{frame}

	\begin{frame}{Simulation Results - bspline FPCR ($n_{harm}$ = 2)}\label{Simulation2}
		\begin{table}
			\centering
			\resizebox*{\columnwidth}{!}{%
				\begin{tabular}{llllllll}
					\cline{2-7}
					& \boldmath{$f_1$}\textbf{, error 1}                 & \boldmath{$f_1$}\textbf{, error 2}                  & \boldmath{$f_2$}\textbf{, error 1}                    & \boldmath{$f_2$}\textbf{, error 2}                 & \textbf{expl. variance} & \textbf{n\_basis} &  \\ \cline{2-7}
					& 2.9163                       & 10.8768                       & 0.9599                        & 1.6431                        & 1                & 4                &  \\
					& {\color[HTML]{FE0000} 2.345} & {\color[HTML]{FE0000} 10.585} & 0.8649                        & 1.5631                        & 0.9776           & 5                &  \\
					& 2.4187                       & 10.6889                       & 0.8739                        & 1.5759                        & 0.9556           & 6                &  \\
					& 2.4971                       & 10.7287                       & 0.8625                        & 1.5723                        & 0.9472           & 7                &  \\
					& 2.5799                       & 10.6971                       & 0.8716                        & 1.575                         & 0.9239           & 8                &  \\
					& 2.6828                       & 10.7669                       & 0.853                         & 1.5661                        & 0.9178           & 9                &  \\
					& 2.825                        & 10.7906                       & 0.8304                        & 1.5622                        & 0.8976           & 10               &  \\
					& 2.9082                       & 10.7774                       & {\color[HTML]{FE0000} 0.8237} & {\color[HTML]{FE0000} 1.5424} & 0.906            & 11               &  \\
					& 2.9519                       & 10.8126                       & 0.8286                        & 1.5561                        & 0.9036           & 12               &  \\
					& 2.9972                       & 10.8221                       & 0.8404                        & 1.5551                        & 0.9052           & 13               &  \\
					& 2.9755                       & 10.7706                       & 0.8396                        & 1.5614                        & 0.9074           & 14               &  \\
					& 2.9762                       & 10.7946                       & 0.8476                        & 1.557                         & 0.9058           & 15               &  \\
					& 2.9627                       & 10.8067                       & 0.8609                        & 1.5615                        & 0.9061           & 16          
				\end{tabular}%
			}
		\end{table}
		\hyperlink{Results}{\beamergotobutton{Results}}
	\end{frame}

	\begin{frame}{Simulation Results - fourier FPCR ($n_{harm}$ = 2)}
		\begin{table}
			\centering
			\resizebox*{\columnwidth}{!}{%
				\begin{tabular}{llllllll}
					\cline{2-7}
					& \boldmath{$f_1$}\textbf{, error 1}                 & \boldmath{$f_1$}\textbf{, error 2}                  & \boldmath{$f_2$}\textbf{, error 1}                    & \boldmath{$f_2$}\textbf{, error 2}                 & \textbf{expl. variance} & \textbf{n\_basis} &  \\ \cline{2-7}
					& 0                             & 0                              & 0                             & 0                             & 0       & 1       &  \\
					& {\color[HTML]{FE0000} 2.2059} & {\color[HTML]{FE0000} 11.2438} & 0.8768                        & 1.5528                        & 0.9846  & 3       &  \\
					& 2.2148                        & 11.2567                        & {\color[HTML]{FE0000} 0.8227} & {\color[HTML]{FE0000} 1.5215} & 0.9584  & 5       &  \\
					& 2.2635                        & 11.2662                        & 0.8828                        & 1.5563                        & 0.9489  & 7       &  \\
					& 2.2721                        & 11.2692                        & 0.8811                        & 1.5531                        & 0.9439  & 9       &  \\
					& 2.2797                        & 11.2574                        & 0.879                         & 1.555                         & 0.9397  & 11      &  \\
					& 2.3039                        & 11.2708                        & 0.8887                        & 1.5591                        & 0.9421  & 13      &  \\
					& 2.3248                        & 11.2898                        & 0.8743                        & 1.5514                        & 0.9283  & 15      &  \\
					& 2.3798                        & 11.2957                        & 0.875                         & 1.5511                        & 0.9182  & 17      &  \\
					& 2.4233                        & 11.3049                        & 0.8632                        & 1.5453                        & 0.9167  & 19      &  \\
					& 2.4589                        & 11.3094                        & 0.8619                        & 1.5432                        & 0.9133  & 21      &  \\
					& 2.5306                        & 11.331                         & 0.8562                        & 1.5408                        & 0.9082  & 23      &  \\
					& 2.5752                        & 11.3272                        & 0.8531                        & 1.5393                        & 0.9062  & 25      & 
				\end{tabular}%
			}
		\end{table}
		\hyperlink{Results}{\beamergotobutton{Results}}
	\end{frame}
\end{document}

>>>>

		\begin{itemize}
    		\item Four combinations with different number of cubic bspline basis-function $n_{basis} \in \{4,5, \dots ,25\}$ and fourier functions $\{1,3, \dots, 25\}$ to perform regression using basis expansion and the FPCR approach
			\item Compare results via criteria (CV, Mallows' CP, ...)

@@

	\begin{frame}{Simulation - Interpretation of Results}\label{Results}
		\textbf{Basis Expansion Regression}
		\begin{itemize}
    			\item Smooth function requires smaller number of $n_{basis}$ and vice versa
    			\item Setup with higher noise requires smoother function

    			%\item  Bspline setup performs overall a bit better.
		\end{itemize}

		Performs better on bumpy function with low noise.\\
	\vspace{0.4cm}
		\textbf{Functional Principal Component Regression}
    	\begin{itemize}
    		\item Two Functional-PC enough to explain variation
    		\item Results quite similar, but bspline setup better for smooth function with noisy response

    	\end{itemize}

    	Performs better in the noisy setup with the smooth function.\\
    	\vspace{0.4cm}

@@

	\begin{frame}{Application Setup}
	Use insights from the simulation study to \textbf{predict the Octane Ratings}.
	\vspace{0.4cm}
		\begin{itemize}
			\item Similar setup, but relying on the initial 60 spectral curves
			\item Validation set approach:	Scores of test data needs to be estimated by the training data
			\item Report results by \textbf{IMSE} for the evaluated best model specifications
		\end{itemize}
	\end{frame}

@@

	\begin{frame}{Simulation Results - bspline basis expansion}\label{Simulation}
		\begin{table}
			\centering
			\resizebox*{8cm}{!}{%
				\begin{tabular}{lllllll}
					\cline{2-6}
					& \boldmath{$f_1, Y_1$}                 & \boldmath{$f_1, Y_2$}                  & \boldmath{$f_2, Y_1$}                    & \boldmath{$f_2, Y_2$}               & \textbf{n\_basis} &  \\ \cline{2-6}
					& 2.1318                        & {\color[HTML]{FE0000} 71.71} & 0.6082                        & 1.5345                        & 4                &  \\
					& 2.0076                        & 71.9395                      & 0.3427                        & 1.2906                        & 5                &  \\
					& {\color[HTML]{FE0000} 1.9937} & 72.2563                      & 0.2456                        & 1.2014                        & 6                &  \\
					& 2.0365                        & 73.7857                      & 0.2797                        & 1.2495                        & 7                &  \\
					& 2.1861                        & 79.0485                      & 0.1044                        & 1.1458                        & 8                &  \\
					& 2.0511                        & 74.1784                      & 0.0356                        & {\color[HTML]{FE0000} 1.0217} & 9                &  \\
					& 2.1052                        & 76.1884                      & 0.0297                        & 1.0393                        & 10               &  \\
					& 2.1012                        & 76.4031                      & {\color[HTML]{FE0000} 0.0296} & 1.0425                        & 11               &  \\
					& 2.3815                        & 86.1707                      & 0.037                         & 1.1819                        & 12               &  \\
					& 2.2114                        & 80.6208                      & 0.0363                        & 1.1024                        & 13               &  \\
					& 2.4495                        & 87.6977                      & 0.038                         & 1.2126                        & 14               &  \\
					& 2.2887                        & 83.4755                      & 0.0315                        & 1.1363                        & 15               &  \\
					& 2.5491                        & 93.593                       & 0.0352                        & 1.2652                        & 16               
				\end{tabular}%
			}
		\end{table}
		\hyperlink{Results}{\beamergotobutton{Results}}
	\end{frame}

	\begin{frame}{Simulation Results - Fourier basis expansion}
		\begin{table}
			\centering
			\resizebox*{8cm}{!}{%
				\begin{tabular}{lllllll}
					\cline{2-6}
					& \boldmath{$f_1, Y_1$}                 & \boldmath{$f_1, Y_2$}                  & \boldmath{$f_2, Y_1$}                    & \boldmath{$f_2, Y_2$}               & \textbf{n\_basis} &  \\ \cline{2-6}

					& 2.0292                       & {\color[HTML]{FE0000} 72.0085} & 0.512                        & 1.4747                        & 3                &  \\
					& {\color[HTML]{FE0000} 2.022} & 72.6017                        & 0.1616                       & 1.1375                        & 5                &  \\
					& 2.0355                       & 73.1836                        & 0.0293                       & {\color[HTML]{FE0000} 0.9907} & 7                &  \\
					& 2.062                        & 73.9631                        & {\color[HTML]{FE0000} 0.029} & 0.9994                        & 9                &  \\
					& 2.0881                       & 75.0921                        & 0.0291                       & 1.0139                        & 11               &  \\
					& 2.0997                       & 75.9422                        & 0.0294                       & 1.0291                        & 13               &  \\
					& 2.1087                       & 76.7123                        & 0.0298                       & 1.0371                        & 15               &  \\
					& 2.1301                       & 77.4908                        & 0.03                         & 1.0398                        & 17               &  \\
					& 2.1535                       & 78.3943                        & 0.0303                       & 1.0509                        & 19               &  \\
					& 2.1775                       & 79.2058                        & 0.0307                       & 1.0617                        & 21               &  \\
					& 2.2058                       & 80.3801                        & 0.031                        & 1.077                         & 23               &  \\
					& 2.2372                       & 81.509                         & 0.0315                       & 1.0905                        & 25               & 
				\end{tabular}%
			}
		\end{table}
		\hyperlink{Results}{\beamergotobutton{Results}}
	\end{frame}

	\begin{frame}{Simulation Results - Bspline FPCR ($n_{harm}$ = 2)}\label{Simulation2}
		\begin{table}
			\centering
			\resizebox*{9cm}{!}{%
				\begin{tabular}{llllllll}
					\cline{2-7}
					& \boldmath{$f_1, Y_1$}                 & \boldmath{$f_1, Y_2$}                  & \boldmath{$f_2, Y_1$}                    & \boldmath{$f_2, Y_2$}                & \textbf{expl. var} & \textbf{n\_basis} &  \\ \cline{2-7}
					& 2.9163                       & 10.8768                       & 0.9599                        & 1.6431                        & 1                & 4                &  \\
					& {\color[HTML]{FE0000} 2.345} & {\color[HTML]{FE0000} 10.585} & 0.8649                        & 1.5631                        & 0.9776           & 5                &  \\
					& 2.4187                       & 10.6889                       & 0.8739                        & 1.5759                        & 0.9556           & 6                &  \\
					& 2.4971                       & 10.7287                       & 0.8625                        & 1.5723                        & 0.9472           & 7                &  \\
					& 2.5799                       & 10.6971                       & 0.8716                        & 1.575                         & 0.9239           & 8                &  \\
					& 2.6828                       & 10.7669                       & 0.853                         & 1.5661                        & 0.9178           & 9                &  \\
					& 2.825                        & 10.7906                       & 0.8304                        & 1.5622                        & 0.8976           & 10               &  \\
					& 2.9082                       & 10.7774                       & {\color[HTML]{FE0000} 0.8237} & {\color[HTML]{FE0000} 1.5424} & 0.906            & 11               &  \\
					& 2.9519                       & 10.8126                       & 0.8286                        & 1.5561                        & 0.9036           & 12               &  \\
					& 2.9972                       & 10.8221                       & 0.8404                        & 1.5551                        & 0.9052           & 13               &  \\
					& 2.9755                       & 10.7706                       & 0.8396                        & 1.5614                        & 0.9074           & 14               &  \\
					& 2.9762                       & 10.7946                       & 0.8476                        & 1.557                         & 0.9058           & 15               &  \\
					& 2.9627                       & 10.8067                       & 0.8609                        & 1.5615                        & 0.9061           & 16          
				\end{tabular}%
			}
		\end{table}
		\hyperlink{Results}{\beamergotobutton{Results}}
	\end{frame}

	\begin{frame}{Simulation Results - Fourier FPCR ($n_{harm}$ = 2)}
		\begin{table}
			\centering
			\resizebox*{9cm}{!}{%
				\begin{tabular}{llllllll}
					\cline{2-7}
					& \boldmath{$f_1, Y_1$}                 & \boldmath{$f_1, Y_2$}                  & \boldmath{$f_2, Y_1$}                    & \boldmath{$f_2, Y_2$}                & \textbf{expl. var} & \textbf{n\_basis} &  \\ \cline{2-7}

					& {\color[HTML]{FE0000} 2.2059} & {\color[HTML]{FE0000} 11.2438} & 0.8768                        & 1.5528                        & 0.9846  & 3       &  \\
					& 2.2148                        & 11.2567                        & {\color[HTML]{FE0000} 0.8227} & {\color[HTML]{FE0000} 1.5215} & 0.9584  & 5       &  \\
					& 2.2635                        & 11.2662                        & 0.8828                        & 1.5563                        & 0.9489  & 7       &  \\
					& 2.2721                        & 11.2692                        & 0.8811                        & 1.5531                        & 0.9439  & 9       &  \\
					& 2.2797                        & 11.2574                        & 0.879                         & 1.555                         & 0.9397  & 11      &  \\
					& 2.3039                        & 11.2708                        & 0.8887                        & 1.5591                        & 0.9421  & 13      &  \\
					& 2.3248                        & 11.2898                        & 0.8743                        & 1.5514                        & 0.9283  & 15      &  \\
					& 2.3798                        & 11.2957                        & 0.875                         & 1.5511                        & 0.9182  & 17      &  \\
					& 2.4233                        & 11.3049                        & 0.8632                        & 1.5453                        & 0.9167  & 19      &  \\
					& 2.4589                        & 11.3094                        & 0.8619                        & 1.5432                        & 0.9133  & 21      &  \\
					& 2.5306                        & 11.331                         & 0.8562                        & 1.5408                        & 0.9082  & 23      &  \\
					& 2.5752                        & 11.3272                        & 0.8531                        & 1.5393                        & 0.9062  & 25      & 
				\end{tabular}%
			}
		\end{table}
		\vspace{0.2cm}
		\hyperlink{Results}{\beamergotobutton{Results}}
	\end{frame}
\end{document}
